Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-04 reanalysis-5-outcome_analysis-interaction.qmd
shared test

if (file.exists(models_cache_file) && !force_refit_models) {
  # Load cached models
  cached_models <- readRDS(models_cache_file)
  models <- cached_models$models
  model_summaries <- cached_models$model_summaries
  model_progress <- cached_models$model_progress
  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
  log_message("Models loaded from cache: ", cache_location)
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE
  models <- list()
  model_summaries <- list()

@@

  # Save to cache
  cached_models <- list(
    models = models,
    model_summaries = model_summaries,
    model_progress = model_progress,
    formula_used = interaction_formula,
    n_imputations = n_imputations,
    timestamp = Sys.time()
  )

  saveRDS(cached_models, models_cache_file)
  cache_location <- models_cache_file
  log_message("Models fitted and saved to cache: ", cache_location)
}

>>>>

if (file.exists(models_cache_file) && !force_refit_models) {
  # Load cached models structure
  cached_data <- readRDS(models_cache_file)

  # Extract components from the cached structure
  models <- cached_data$models
  model_progress <- cached_data$model_progress

  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
  log_message(paste0("Models loaded from cache: ", cache_location))
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE
  models <- list()
  model_summaries <- list()

@@

  # Save to cache with full structure
  cached_data <- list(
    models = models,
    model_progress = model_progress,
    formula_used = interaction_formula,
    n_imputations = n_imputations,
    timestamp = Sys.time()
  )
  saveRDS(cached_data, models_cache_file)
  cache_location <- models_cache_file
  log_message("Models fitted and saved to cache: ", cache_location)
}
